An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-16 main.tex
Add a small discussion for longer ranking tables

When $N=2$ the Moran process is effectively a measure of the distribution of relative
mean payoffs over all possible matches between two players. The strategy
that scores higher than the other more often will fixate more often. For \(N=2\)
the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
considered separately for larger \(N\) in sections~\ref{sec:strong_invaders}
and~\ref{sec:strong_resistors}. Figure~\ref{fig:boxplot_2} shows all fixation
probabilities for the strategies considered. This is summarised in
Table~\ref{tbl:summary_top_2}.

@@

@@

The top strategies are given in Tables~\ref{tbl:top_invade}.

@@

It can be seen that apart from CS, none of the strategies
of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 14\}\). The new
high performing strategies are:

@@

As well as noting that the memory length and complexity of these strategies are
much greater than one, it is interesting to note that none of them are akin to
memory one strategies. Only one is stochastic although close inspection of the
source code of PSO Gambler shows that it makes stochastic decisions rarely, and
is functionally very similar to its deterministic cousin Evolved Looker Up. Apart
from TF3 in \(N=3\), the finite state machines trained specifically for Moran
processes do not appear in the top 5 while strategies trained for tournaments do.
This is due to the nature of invasion: most of the opponents will initially be of
different types. The next section will consider the converse situation.

>>>>

When $N=2$ the Moran process is effectively a measure of the distribution of relative
mean payoffs over all possible matches between two players. The strategy
that scores higher than the other more often will fixate more often. For \(N=2\)
the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
considered separately for larger \(N\) in sections~\ref{sec:strong_invaders}
and~\ref{sec:strong_resistors}. Figure~\ref{fig:boxplot_2} shows all fixation
probabilities for the strategies considered. The top 16 (10\%) strategies are
shown in
Table~\ref{tbl:summary_top_2}. The top five ranking strategies are:

@@

It is also noted that TF1, TF2 and TF3 all perform well, other finite state
machines include Prober 3 and Prober 4 which are described in \cite{prison}.
This is also the \(N\) for which a zero determinant strategy does appear in the
top 10\% ranking strategies: ZD-extort-4. The performance of zero determinant
strategies will be examined more closely in Section~\ref{sec:population_size}.

@@

The top 16 strategies are given in Tables~\ref{tbl:top_invade}.

@@

It can be seen that apart from CS, none of the strategies
of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 14\}\). The new
top performing strategies are:

@@

Only one of the above strategies is stochastic although close inspection of the
source code of PSO Gambler shows that it makes stochastic decisions rarely, and
is functionally very similar to its deterministic cousin Evolved Looker Up.
The PSO Gambler Mem1 strategy is a memory one strategy that has been trained to
maximise it's utility and does perform well.
Apart from TF3, the finite state machines trained specifically for
Moran processes do not appear in the top 5: whereas strategies trained for
tournaments do. This is due to the nature of invasion: most of the opponents
will initially be different strategies. The next section will consider the
converse situation.
